Stack Safety as a Security Property

### 2020-07-08 main.tex
Actually add the changes

Adopting that model, however, poses another novel challege: not only
does a caller need to be protected from its callee, but the callee
itself needs to be protected from {\em its} callees: the notion of
``attacker'' changes throughout the execution of a program!

\bcp{Again, here, a bigger transition, more setup, and a longer
  discussion are needed.  This is really the crux of what we are
  doing!} \leo{Attempt}
%
Moreover, applying the standard language-based-security notions of
integrity and confidentiality in the stack-safety setting raises a
novel challenge: the notion of ``attacker'' changes during execution.
Not only does a caller need to be protected from its callee, but the
callee itself needs to be protected from {\em its} callees. We address
this problem by using a similarly changing notion of accessibility for
the different components of the machine: we adjust the integrity and
confidentiality level of different stack locations and registers at
every transition (call or return) between functions.  \bcp{that's way too
  terse!}\leo{Slightly better, still needs a bit probably}
%\apt{connection to ``attacker'' still vague.}  \rb{Mention
%  to varying ``accessing power'' of the attacker?  The notion of
%  attacker changes on certain actions that are not externally
%  visible.} \bcp{Maybe the best way is to grab the bull by the horns:
%  ``If we're going to phrase stack safety as a security property, we
%  need to talk about an attacker model, and this is where the
%  technicalities get really interesting...''}

>>>>

Adopting that model in our setting, however, poses another novel
challege: not only does a caller need to be protected from its callee,
but the callee itself needs to be protected from {\em its}
callees. That is, the notion of ``attacker'' changes throughout the
execution of a program!  We address this problem by using a similarly
changing notion of accessibility for the different components of the
machine: we adjust the integrity and confidentiality level of
different stack locations and registers at every transition (call or
return) between functions.  \bcp{that's way too terse!}\leo{Slightly
  better, still needs a bit probably}
%\apt{connection to ``attacker'' still vague.}  \rb{Mention
%  to varying ``accessing power'' of the attacker?  The notion of
%  attacker changes on certain actions that are not externally
%  visible.} \bcp{Maybe the best way is to grab the bull by the horns:
%  ``If we're going to phrase stack safety as a security property, we
%  need to talk about an attacker model, and this is where the
%  technicalities get really interesting...''}
